\documentclass{article}
\usepackage{amsmath,amsthm,amsfonts, amssymb}
\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}
\usetikzlibrary{decorations.text,calc}

\setlength{\textheight}{8.5in}
\setlength{\evensidemargin}{0.0in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\topmargin}{-0.5in}
\setlength{\textwidth}{6.5in}

\usepackage{prooftree}
\usepackage{boxproof}
\usepackage{parskip}

\newcommand{\handout}[6]{
   \renewcommand{\thepage}{#1-\arabic{page}}
   \noindent
   \begin{center}
      \vbox{
    \hbox to \textwidth { #2 \hfill #3 }
       \vspace{4mm}
       \hbox to \textwidth { {\Large \hfill #4  \hfill} }
       \vspace{4mm}
       \hbox to \textwidth { { #5 \hfill #6} }
      }
   \hrulefill
   \end{center}
   \vspace*{4mm}
}
\begin{document}
\handout{}{CS 512: Formal Methods}{Spring 2016}{Assignment 9: Modeling with CTL}{Instructor: Assaf Kfoury}{Author: Patrick Gomes}
\section{Problem 1}
e) Yes it is satisfiable with a $\delta$ of 0.001, the answer is x = y = 0.0008217490086014628 given by dReal
\\f) No it is no longer satisfiable.
\\g) If you allow a $\delta$ of 0.2 then the solution is satisfiable. dReal has given back: x = 0.3622065017492991 and y = 0.3543384320284063 which are within our delta bounds.

\section{Problem 2}
Defining 'right' to be equivalent to i + 1 unless i = 5 in which case right is i = 1.\\ \\
a) $AG\ \neg (w_1 \land w_2 \land w_3 \land w_4 \land w_5)$
\\ \text{From now onwards, it is never the case that all philosophers are waiting.}\\
\\b) $AG (AF e_1 \land AF e_2 \land AF e_3 \land AF e_4 \land AF e_5)$
\\ \text{From now onwards, all philosophers will eventually eat.}\\
\\b) $AG (AF e_1 \land AF e_2 \land AF e_3 \land AF e_4 \land AF e_5)$
\\ \text{From now onwards, all philosophers will eventually eat (i.e. not starve to death).}\\

d) $AG( (e_1 \to AF e_2) \land (e_2 \to AF e_3) \land (e_3 \to AF e_4) \land (e_4 \to AF e_5) \land (e_5 \to AF e_1) $
\\ \text{If a philosopher can eat, then at some point in the future the philosopher to his right will be able to eat.}\\

e)\ $AG (AF e_1 \lor AF e_2 \lor AF e_3 \lor AF e_4 \lor AF e_5)$
\\ \text{From now onwards, some philosopher will be able to eat in the future.}\\ 

f)\ $AG (AF e_1 \land AF e_2 \land AF e_3 \land AF e_4 \land AF e_5)$ 
\\ \text{From now onwards, all philosophers will inevitably eat in the future.}\\

g)\ $AG ((e_1 \to \neg (e_2 \land e_5)) \land  (e_2 \to \neg (e_1 \land e_3)) \land  (e_3 \to \neg (e_2 \land e_4)) \land  (e_4 \to \neg (e_3 \land e_5)) \land  (e_5 \to \neg (e_4 \land e_1))) $
\\ \text{From now onwards, if a philosopher is eating, the philosophers to his left and right can't be eating.}\\

h)\ $AG (e_1 \lor e_2 \lor e_3 \lor e_4 \lor e_5)$
\\ \text{From now onwards, at least one philosopher is always eating.}\\

\section{Problem 3}
a)\\
All available states:
\begin{align*}
	s_0 - (f,f,f,f,f)\\
	s_1 - (t,f,f,f,f)\\
	s_2 - (t,f,t,f,f)\\
	s_3 - (t,f,f,t,f)\\
	s_4 - (f,t,f,f,f)\\
	s_5 - (f,t,f,t,f)\\
	s_6 - (f,t,f,f,t)\\
	s_7 - (f,f,t,f,f)\\
	s_8 - (f,f,t,f,t)\\
	s_9 - (f,f,f,t,f)\\
	s_{10} - (f,f,f,f,t)\\
\end{align*}
State transitions for each state:
\begin{align*}
	s_0 -> \text{all states}\\
	s_1 -> \{s_0, s_4, s_5, s_6, s_7, s_8, s_9, s_{10}\}\\
	s_2 -> \{s_0, s_4, s_5, s_6, s_9, s_{10}\}\\
	s_3 -> \{s_0, s_4, s_6, s_7, s_8, s_9, s_{10}\}\\
	s_4 -> \{s_0, s_1, s_2, s_3, s_7, s_8, s_9, s_{10}\}\\
	s_5 -> \{s_0, s_1, s_2, s_7, s_8, s_9, s_{10}\}\\
	s_6 -> \{s_0, s_1, s_2, s_3, s_7, s_9\}\\
	s_7 -> \{s_0, s_1, s_3, s_4, s_5, s_6, s_9, s_{10}\}\\
	s_8 -> \{s_0, s_1, s_3, s_4, s_5, s_9\}\\
	s_9 -> \{s_0, s_1, s_2, s_4, s_6, s_7, s_8, s_{10}\}\\
	s_{10} -> \{s_0, s_1, s_2, s_3, s_4, s_5, s_7, s_9\}
\end{align*}
b)
The first CTL is not satisfied because the path $s_0, s_3$ violates it.\\
The second CTL is not satisfied because the path$s_0, s_1$ violates it. \\
The third CTL is satisfied!
\\ \\c)
All you need to do is add an intermediate set of states such that after eating you go to a state where your value for f is true and then it resets back to waiting to eat.
\end{document}