\documentclass{article}
\usepackage{amsmath,amsthm,amsfonts, amssymb}
\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{decorations.text,calc}


\setlength{\textheight}{8.5in}
\setlength{\evensidemargin}{0.0in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\topmargin}{-0.5in}
\setlength{\textwidth}{6.5in}


\newcommand{\handout}[6]{
   \renewcommand{\thepage}{#1-\arabic{page}}
   \noindent
   \begin{center}
      \vbox{
    \hbox to \textwidth { #2 \hfill #3 }
       \vspace{4mm}
       \hbox to \textwidth { {\Large \hfill #4  \hfill} }
       \vspace{4mm}
       \hbox to \textwidth { { #5 \hfill #6} }
      }
   \hrulefill
   \end{center}
   \vspace*{4mm}
}

\begin{document}

\handout{}{CS 512: Formal Methods}{Spring 2016}{Assignment 4: Formal Modeling in Propositional Logic and in QBF Logic}{Instructor: Assaf Kfoury}{Author: Patrick Gomes}

\section{Problem 1}
P = \{a, b, c\} and S = \{1, 2, 3\}\\

a) 
\begin{align*}
	\bigwedge_{i\in P}  ( \bigvee_{j\in S} P_{i,j} )\\
\end{align*}
\text{explanation: for each person i, $P_i,1 \lor P_i,2 \lor P_i,3$ must be true, so they must have a seat.}\\

b)\\
\begin{align*}
	(\bigwedge_{i\in P}  (\bigvee_{j\in S}(P_{i,j} \to \bigwedge_{j`\in S -\{j\}}))) \land (\bigwedge_{j\in S} (\bigvee_{i\in P}(P_{i,j}))))\\
\end{align*}
\text{explanation: first term is exclusive or on seating, only one person can be in a seat. second term is all seats need a person sitting on them.}\\

c)\\
1.
\begin{align*}
	\neg P_{a,2} \land \neg P_{c,2} \land (P_{a,1} \to P_{c,3} )  \land (P_{a,3} \to P_{c,1} )  \land (P_{c,1} \to P_{a,3} )  \land (P_{c,3} \to P_{a,1} ) \\
\end{align*}
\text{explanation: covers all possible cases of where a and c can be and where the other person should be. neither can be in 2.}\\ \\
2.
\begin{align*}
	\neg P_{a,1} 
\end{align*}
3.
\begin{align*}
	(P_{c,1} \land P_{b,3}) \land (P_{c,2} \land P_{b,1}) 
\end{align*}
\text{explanation: assume if c is in 1, b can't be in 2, else if c is in 2, b can't be in 3. covers all cases, if c is in 3, b can be anywhere.}\\ \\

4.
\text{No this isn't possible. a has to be in 3, since a can't be in 1 or 2 from (1) and (2). c can't sit next to a,} \\
\text{so c sits in seat 1. b is left with seat 2 since all seats must be filled, and that violates (3), thus this isn't doable.}\\

\section{Problem 2}
P = \{0,$\dots$,64\} S = \{0,\dots\,32\}\\
a)
\begin{align*}
	\varphi_{m,n,s} \triangleq x_{m,n,s} \land (\bigwedge_{n` \in P - \{n\}} \neg x_{m,n`,s})
\end{align*}
\text{explanation: if m is at spot n, make sure m is nowhere else.}\\ \\
b)
\begin{align*}
	\psi_{m,n,s} \triangleq \{ \varphi_{m,n,s} \to \bigwedge_{m` \in S - \{m\}} \neg \varphi_{m`,n,s}  \ \ | \ \ m \in S, n \in P - \{0\} \ \}
\end{align*}
\text{explanation: if a piece m is at spot n, make sure no piece m` is also in spot n, unless n is spot 0.}\\
\text{$\varphi_{m`,n,s}$ is true only if m` is in spot n at time s.}\\ \\
c)
\begin{align*}
	G_K \triangleq \{   \bigvee_{n \in P - \{0\}} \varphi_{5,n,K}   \} \land \neg \varphi_{29, 0, K}\\
\end{align*}
\text{explanation: we need to check that the white king is alive on 1 space at step K, }\\
\text{and that the black king is off the board (spot 0) at step K}\\ \\

\section{Problem 3}
Not Transitive: \\
\begin{align*}
	S = \{ 1, 2, 3\}, \ 
	R = \{(1,1), (2,2), (3,3), (1,2), (2,1), (2,3), (3,2)\}, \ 
	P(x,y)\ is\ true\ if\ (x,y) \in R\\
	\text{Reflexive and Symmetric are met for all $x\in S$ but $P((1,2)) \land P(2,3) \to P(1,3)$ is false because P(1,3) $\notin$ R}\\
\end{align*}
Not Symmetric:
\begin{align*}
	\text{P(x,y) is true if x $\geq$ y}
\end{align*}
\begin{align*}
	\text{Obviously Reflexive and Transitive, not Symmetric because 2 $\geq$ 1 is true but 1 $\geq$ 2 is false.}\\ 
\end{align*}
Not Reflexive:
\begin{align*}
	\text{P(x,y) is true if x $\neq$ y}
\end{align*}
\begin{align*}
	\text{Obviously not Reflexive because x $\neq$ x is always false. Symmetric because if x $\neq$ y then y $\neq$ x.}
\end{align*}
\begin{align*}
	\text{Transitive because x $\neq$ y $\land$ y $\neq$ z $\to$ x $\neq$ z}\\
\end{align*}


\end{document}